\thetitle

### 2023-05-23 stlc-compiled.tex
fix typos and awkward wordings
Save. Fixing overflow.

Def subst\_tm_unit :=[@\codecomment{\textls[-20]{emmited upon definition of case}}@]

@@

| tm_unit : tm | tm_var : id -> tm
| tm_abs : id -> tm -> tm | tm_app : tm -> tm -> tm.
[@\codecomment{Instantiate \texttt{tm} partial recursor \& its computational behaviors}@]
Def tm_prect_STLC := \lambda P, tm_rect (\lambda[@\,@]t, option (P t)).

>>>>

Def subst\_tm_unit :=[@\codecomment{\textls[-20]{emitted upon definition of case}}@]

@@

| tm_unit | tm_var (v : id) [@\dadada@]
[@\codecomment{Inst. partial recursor \& computational behaviors}@]
Def tm_prect_STLC P := 
      tm_rect (\lambda[@\,@]t, option (P t)).

### 2023-05-23 stlc-mechanized.tex
trying out a name for the language design and impl
Save. Fixing overflow.

\begin{figure}
\begin{minipage}{\textwidth}
\begin{multicols}{2}

@@

\begin{lstlisting}[firstnumber=77]
Family STLCFix extends STLC.[@\tanc{STLCFix-start}@]
[@\hfill\codecomment{STLC extended with fixpoints}@]
FInductive tm : Set +=
| tm_fix : id -> tm -> tm.

FRecursion subst on tm motive \lambda _, id -> tm -> tm.
Case tm_fix := \lambda y t' IHt' x t, [@\dadada@].
End subst.

@@

\end{multicols}
\end{minipage}
\caption{Using our plugin to mechanize STLC and the fixpoints extension,
as envisioned in \cref{fig:stlc-nonmechanized}.}
\label{fig:stlc-mechanized}
\end{figure}

>>>>

\begin{figure}
\vspace{-10pt}
\begin{minipage}{\textwidth}
\begin{multicols}{2}

@@

\begin{lstlisting}[firstnumber=77]
Family STLCFix extends STLC.[@\tanc{STLCFix-start}@]
[@\hfill\codecomment{STLC extended with fixpoints}@]
FInductive tm : Set +=
| tm_fix : id -> tm -> tm.
FRecursion subst on tm 
      motive (\lambda _, id -> tm -> tm).
Case tm_fix := \lambda y t' IHt' x t, [@\dadada@].
End subst.

@@

\end{multicols}
\end{minipage}
\caption{Using \Lang to mechanize STLC and the fixpoints extension,
as envisioned in \cref{fig:stlc-nonmechanized}.}
\label{fig:stlc-mechanized}
\end{figure}

### 2023-05-23 stlcfix-compiled.tex
minor
Save. Fixing overflow.

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Cases\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases
[@\outdent@](self : STLCFix\_subst\_Cases\_Ctx).
Include STLC\_subst\_Cases(self).[@\hfill\codecomment{reuse}@]
Def subst\_tm_fix := [@\dadada@].[@\hfill\codecomment{translation of new case}@]
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_subst\_Cases.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@][@\textls[-30]{STLCFix}@]\_[@\textls[-30]{subst}@]\_[@\textls[-30]{Ctx}@]).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted for other fields defined in \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon conclusion of \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
[@\codecomment{Instantiate \texttt{tm} \& its constructors}@][@\tanc{c-STLCFix-d-tm-start}@]
Inductive tm : Set :=
| tm_unit : tm | tm_var : id -> tm
| tm_abs : id -> tm -> tm | tm_app : tm -> tm -> tm
| tm_fix : id -> tm -> tm.
[@\codecomment{Instantiate \texttt{tm} partial recursors \& their comp.\ behaviors}@] [@\dadada@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
[@\codecomment{Instantiate \texttt{subst} \& its computational behaviors}@]
Def subst := tm_rect _ subst\_tm_unit
subst\_tm_var subst\_tm_abs subst\_tm_app[@\hfill\codecomment{reuse}@]
subst\_tm_fix.
Fact [@\textls[-40]{subst\_tm\_unit\_eq}@] : [@\dadada@]. [@\textls[-40]{{\color{dkblue}reflexivity}.}@] Qed.
Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\codecomment{\textls[-10]{Include\;\texttt{ty}, its constructors, partial recursor, etc.}}@] [@\dadada@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\codecomment{Include/Instantiate other fields of \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
Include STLC\_typesafe.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-typesafe}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

>>>>

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Cases\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases
[@\outdent@](self : STLCFix\_subst\_Cases\_Ctx).
Include STLC\_subst\_Cases(self).[@\hfill\codecomment{reuse}@]
Def subst\_tm_fix := [@\dadada@].[@\hfill\codecomment{translation of new case}@]
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_subst\_Cases.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@][@\textls[-30]{STLCFix}@]\_[@\textls[-30]{subst}@]\_[@\textls[-30]{Ctx}@]).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted for other fields defined in \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon conclusion of \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
[@\codecomment{Instantiate \texttt{tm} \& its constructors}@][@\tanc{c-STLCFix-d-tm-start}@]
Inductive tm : Set :=
| tm_unit | tm_var (v : id)
| tm_abs (v : id) (b : tm) | tm_app (a b : tm)
| tm_fix (v : id) (b : tm).
[@\codecomment{Inst. \texttt{tm} partial recursors \& their comp.\ behaviors}@] [@\dadada@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
[@\codecomment{Instantiate \texttt{subst} \& its computational behaviors}@]
Def subst := tm_rect _ subst\_tm_unit
subst\_tm_var subst\_tm_abs subst\_tm_app[@\hfill\codecomment{reuse}@]
subst\_tm_fix.
Fact [@\textls[-0]{subst\_tm\_unit\_eq}@] : [@\dadada@]. reflexivity. Qed.
Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\codecomment{\textls[-10]{Include\;\texttt{ty}, its constructors, partial recursor, etc.}}@] [@\dadada@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\codecomment{Include/Instantiate other fields of \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
Include STLC\_typesafe.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-typesafe}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}
